The top-level dacman module provides methods and classes for doing
data comparisons at scale. Data can be compared using dacman.diff().

\section{dacman.diff}
\texttt{dacman.diff(new\_file, old\_file, *argv, comparator\_plugin=None)}

Method to perform a single comparison using the specified plugin.

\fbox{
  \parbox{\textwidth}{
  \textbf{Parameters:}\\
  new\_file: path to the new file (data to compare)\\
  old\_file: path to the old file (data compared against)\\
  *args   : optional parameters for specific comparisons\\
  comparator\_plugin: plugin to be used for comparing the files\\

  \textbf{Returns:} None
 }
}

\section{dacman.DataDiffer}
\texttt{class dacman.DataDiffer(comparisons, executor=Executor.DEFAULT)}

Class that compares multiple files or objects. It takes
a list of comparisons and performs the comparisons in
parallel. The executor argument specifies the type of
runtime to be used for doing the comparisons.

\subsection{use\_plugin(plugin)}
%\texttt{dacman.DataDiffer.use\_plugin(plugin)}

Method to set a specific plug-in for camparing the files.
If no plug-in is set, then \systemname will select one
of the internal plug-ins based on file/data types.

\subsection{start()}
%\texttt{dacman.DataDiffer.start()}

Method to start the comparison using the specified runtime and
plug-in. 

\subsection{mpi\_communicator}
%\texttt{dacman.DataDiffer.mpi\_communicator}

Attribute specifying the MPI communicator to be used when using
the MPI executor.

\section{dacman.Executor}
\texttt{class dacman.Executor}

Types of runtime in \systemname.

\fbox{
  \parbox{\textwidth}{
        DEFAULT  : A single threaded runtime.\\
        THREADED : Runtime based on Python's multiprocessing.\\
        MPI      : MPI based.\\
        TIGRES   : Tigres workflow management system. \\
  }
}

\section{dacman.plugins} 
\texttt{dacman.plugins.default.DefaultPlugin}

Module containing the system and user-defined plugins.
