\section{Overview}
Scientific datasets are updated frequently due to changes in
instrument configuration, software updates, quality assessments
or data cleaning algorithms. However, due to the large size and
complex data structures of these datasets, existing tools either
do not scale or are unable to generate meaningful change information.

The \textbf{\systemname} (\textbf{DA}ta \textbf{C}hange \textbf{Man}agement)
framework allows users to efficiently and effectively identify,
track and manage data change and associated provenance in scientific
datasets. There are two main components of \systemname:
\begin{itemize}
\item Change tracker that keeps track of the changes between
 different versions of a dataset.
\item Query manager that manages data change related queries.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Features}
The key features of \systemname include:
\begin{itemize}
\item HPC support. \systemname provides MPI support for enabling parallel
 change capture in HPC environments.
\item Offline comparison. Datasets can be compared away from the actual
 location of the data, allowing users to find changes without necessarily
 moving the datasets to a common location.
\item Extendable. Users can plug-in their own scripts to calculate changes.
\item Flexible command-line options. Provides different options to configure
 change detection.
\item Detailed output. \systemname outputs contain details on the different
 types and amount of change.
\item Customizable logging. Users can customize where and what to log,
 including the detailed steps in the change capture process.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Requirements}
\systemname is developed using Python. It requires Python 2.7 or greater.
Users need Python setuptools and pip to install \systemname. Fore detailed
instructions on the installation, please refer to Chapter~\ref{ch:install}.

\systemname is known to work on the following operating systems:
\begin{itemize}
\item Linux
\item Unix-like OSs
\item Mac OS
\end{itemize}
